---
title: "1.1 — Introduction and Overview — Class Content"
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance=minimal}
# Meeting Dates
*Tuesday, August 23, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Welcome to ECON 452 — History of Economic Thought! Today’s lesson will be an introduction to the course and a bit about why the history of economics matters, explain in part by looking at the profession of economics today. Please read and familiarize yourself with the [syllabus](/syllabus).

## <i class="fas fa-book-reader fa-lg"></i> Readings

This week we will be covering elements of:

- <i class="fas fas fa-book"></i> Ch.1 in Landreth and Colander
- <i class="fas fas fa-book"></i> Ch.1 in Blaug 1996

I recommend reading this to get acquainted with some of the big picture ideas and debates we are going to wrestle with this semester, as well as the state of economics today. Regarding economics today, here are some articles that I mention in today’s class:

- [<i class="fas fa-file-pdf"></i> Boettke, Fink, and Smith, 2012, "The Impact of Nobel Prize Winners in Economics: Mainline vs. Mainstream"](/readings/Boettke-Fink-Smith-2012.pdf)
- [<i class="fas fa-file-pdf"></i> Colander, 2015, "Intellectual Incest on the Charles: Why Economists are a little bit off"](/readings/Colander-2015.pdf)
- [<i class="fas fa-file-pdf"></i> Cawley, 2018, "A Guide and Advice for Economists on the U.S. Junior Academic Job Market, 2018-2019 Edition"](/readings/Cawley-2018.pdf)
- [<i class="fas fa-file-pdf"></i> Heckman and Moktan, 2020, "Publishing and Promotion in Economics: The Tyranny of the Top Five"](/readings/Heckman-Moktan-2020.pdf)

Please note going forward, the lesson numbers and topics (e.g. 1.1) on this website are *my* design, and will not match up with the textbook!

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides. 

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("1.1-slides")
```