---
title: "1.2 — What Exactly is Economics? — Class Content"
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance=minimal}
# Meeting Dates
*Thursday, August 25, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we discuss some common themes we will encounter this semester, and take a broad philosophical approach to what economics is and how it has developed.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

NONE

### Recommended Readings

This week we will be covering elements of:

- <i class="fas fas fa-book"></i> Ch.1 (Introduction) in Landreth and Colander
- <i class="fas fas fa-book"></i> Preface & Ch.17 (Methodological Postscript) in Blaug 1996 

Other helpful readings:

- [<i class="fas fa-file-pdf"></i> Buchanan, 1964, “What Should Economists Do?”](/files/readings/McCloskey-1998.pdf)
- [<i class="fas fa-file-pdf"></i> Blaug, 1975, "Kuhn versus Lakatos, or paradigms versus research programmes in the history of economics"](/files/readings/Blaug-1975.pdf)
- [<i class="fas fa-file-pdf"></i> McCloskey, 1998, *The Rhetoric of Economics* pp.20-28](/files/readings/McCloskey-1998.pdf)

The following Wikipedia entries can also provide more background on the philosophy of science (broadly in order):

- [<i class="fab fa-wikipedia-w"></i> Philosophy of Science](https://en.wikipedia.org/wiki/Philosophy_of_science)
- [<i class="fab fa-wikipedia-w"></i> Positivism](http://en.wikipedia.org/wiki/Positivism)
- [<i class="fab fa-wikipedia-w"></i> Logical Positivism](https://en.wikipedia.org/wiki/Logical_positivism)
- [<i class="fab fa-wikipedia-w"></i> Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper)
- [<i class="fab fa-wikipedia-w"></i> Thomas Kuhn](https://en.wikipedia.org/wiki/Thomas_Kuhn)
- [<i class="fab fa-wikipedia-w"></i> Imre Lakatos](https://en.wikipedia.org/wiki/Imre_Lakatos)
https://en.wikipedia.org/wiki/Imre_Lakatos
- [<i class="fab fa-wikipedia-w"></i> Lionel Robbins on Economics](https://en.wikipedia.org/wiki/An_Essay_on_the_Nature_and_Significance_of_Economic_Science)
- [<i class="fab fa-wikipedia-w"></i> Milton Friedman on Positivist Methodology](https://en.wikipedia.org/wiki/Essays_in_Positive_Economics)

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides. 

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("1.2-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

We will start getting the discussion board up and running this week on Blackboard. As a trial week, you will all get full points this week.