---
title: "1.4 — Medieval Religious Writers — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, September 1, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we discuss the Medieval writers.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

<iframe width="980" height="550" src="https://www.youtube.com/embed/t2c-X8HiBng" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

- <i class="fas fas fa-book"></i> St. Thomas Aquinas & skim *Summa Theologica* in *Reader*
- <i class="fas fas fa-book"></i> Ch.2 (Early Preclassical Economic Thought) in Landreth & Colander

Blaug unfortunately does not cover anything before mercantilism & the physiocrats.

### Recommended Readings:

The following Wikipedia entries can also provide more background on these writers and their famous works:

- [<i class="fab fa-wikipedia-w"></i> Thomas Aquinas](https://en.wikipedia.org/wiki/Thomas_Aquinas)
- [<i class="fab fa-wikipedia-w"></i> Ibn Khaldun](https://en.wikipedia.org/wiki/Ibn_Khaldun)

- Al-Hamdi, 2006, [Ibn Khaldun: The Father of the Division of Labor](https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.515.2885&rep=rep1&type=pdf)

### Questions to Help Your Reading

- What topics does Aquinas cover in his writings?
- What questions is he interested in?
- What is his style of inquiry?
- What does he say about whether prices are "just"?
- What is his view on usury?
- How does he engage with "the philosopher" (Aristotle)?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("1.4-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Sep 2

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday September 2.
