---
title: "1.5 — Mercantilism — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, September 6, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

We are entering the era of mercantilism, and will spend at least a week in this era before we get to the Classical economists. There are a lot of well-develoepd writings from a lot of well-known thinkers of this era. Since we will not be lingering long, there is a lot of reading in a short amount of time. Thus, it's most important that you read the *secondary* textbook, and in the *Reader*, read the biographies of Mun, Petty, and Mandeville, and then *skim* each of their writings to get a feel for what they are interested in and how they discuss it. 

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Thomas Mun, William Petty, Bernard de Mandeville^[Yes, this is a little out of order] & *skim* each's writings in *Reader*
- <i class="fas fas fa-book"></i> Ch.3 Early Preclassical Economic Thought up through Physiocracy (p.56) in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.1 Pre-Adamite Economics up through Physiocracy (p.24) in Blaug

Blaug unfortunately does not cover anything before mercantilism & the physiocrats.

### Recommended Readings:

The following Wikipedia entries can also provide more background on these writers and their famous works:

- [<i class="fab fa-wikipedia-w"></i> Mercantilism](https://en.wikipedia.org/wiki/Mercantilism)
- [<i class="fab fa-wikipedia-w"></i> Thomas Mun](https://en.wikipedia.org/wiki/Thomas_Mun)
- [<i class="fab fa-wikipedia-w"></i> William Petty](https://en.wikipedia.org/wiki/William_Petty)
- [<i class="fab fa-wikipedia-w"></i> Bernard Mandeville](https://en.wikipedia.org/wiki/Bernard_Mandeville)

### Questions to Help Your Reading

- *Who* are the mercantlists, and why are they writing?
- What are the mercantilists interested in?
- What are the policy prescriptions of the mercantilists?
- How do the mercantlists view human nature?
- What is the role of government according to the mercantilists?
- What aspects of mercantilism are still present today?
- What does modern economics think of mercantilist ideas?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("1.5-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Sep 9

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday September 9.
