---
title: "2.1 — David Hume and Adam Smith the Philosopher — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, September 20, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we discuss Hume and begin Smith.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> David Hume, *Political Discourses*, and Adam Smith (but not *WON* yet) in *Reader*

### If You Hadn't Yet:
- <i class="fas fas fa-book"></i> Start Ch.4 "Adam Smith" in Landreth & Colander
- <i class="fas fas fa-book"></i> Start Ch.2 "Adam Smith" in Blaug

### Recommended Readings:

The following Wikipedia entries can also provide more background on these writers and their famous works:

- [<i class="fas fa-podcast"></i> *Econtalk*: Dennis Rasmussen on Hume and Smith and The Infidel and the Professor](https://www.econtalk.org/dennis-rasmussen-on-hume-and-smith-and-the-infidel-and-the-professor/)
- [<i class="fas fa-podcast"></i> *Econtalk*: Russ Roberts and Mike Munger on How Adam Smith Can Change Your Life](https://www.econtalk.org/dennis-rasmussen-on-hume-and-smith-and-the-infidel-and-the-professor/)
- [<i class="fas fas fa-book"></i> Roberts, *How Adam Smith Can Change Your Life: An Unexpected Guide to Human Nature and Happiness*](https://www.amazon.com/gp/product/1591847958)
- [<i class="fab fa-wikipedia-w"></i> David Hume](https://en.wikipedia.org/wiki/David_Hume)
- [<i class="fab fa-wikipedia-w"></i> Adam Smith](https://en.wikipedia.org/wiki/Adam_Smith)
- [<i class="fab fa-wikipedia-w"></i> Theory of Moral Sentiments](https://en.wikipedia.org/wiki/The_Theory_of_Moral_Sentiments)

### Questions to Help Your Reading

- Is David Hume a mercantilist, a Classical economist, or some mix? (Your textbooks seem to disagree!)
- What do Hume and Smith mean by "sentiments?"
- How does Hume approach money? In what ways is his quantity theory of money similar to, and different from, John Locke's?
- What is Hume's "price-specie flow mechanism"? How does this connect with a gold standard (or similar commodity-based money)?
- How does Hume criticize mercantilism?
- According to Hume, where does interest come from, and how are interest rates determined? Is it based on the money supply, as some mercantilists supposed?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.1-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Sep 23

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday September 23.

## Tournament Votes

The first round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
