---
title: "2.3 — Smithean Price Theory & Economic Growth — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, September 27, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we dive into Smith's analytical system, and some may say, the first organized discussion of economic analysis. The reading for Smith comes primarily from Book I: *Of the Causes of Improvement in the productive Powers of Labour* and Book II *Of the Nature, Accumulation, and Employment of Stock* and a little bit from Book V: *Of the Revenue of the Sovereign or Commonwealth*. Your reader focuses primarily on Book I and the division of labor (pp.156-165), which is great, but sadly lacks selections on capital from Book II or public finance from Book V. 

It is a good idea whenever you can, to read as much of Books I^[You can skip Smith's difficult digression on silver in Chapter 11.] and II as you can. You can find all of *The Wealth of Nations* online for free here:

- [<i class="fas fas fa-book"></i> Wealth of Nations (Online)](https://www.econlib.org/library/Smith/smWN.html)

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> Adam Smith's *Wealth of Nations*: Books I-II excerpts in *Reader* (pp.156-165)

###  If You Hadn't Yet:
- <i class="fas fas fa-book"></i> Ch.4 "Adam Smith" in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.2 "Adam Smith" in Blaug


Lastly, note the following useful tidbit, although he does use both words occasionally, “stock” is Adam Smith's word for “capital.”

### Recommended Readings:

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Adam Smith](https://en.wikipedia.org/wiki/Adam_Smith)
- [<i class="fab fa-wikipedia-w"></i> The Wealth of Nations](https://en.wikipedia.org/wiki/The_Wealth_of_Nations)

### Questions to Help Your Reading

#### Book I

- What is/are the “wealth of nations”?
- What is the division of labor? What limits or augments it?
- Explain Adam Smith's famous pin factory example, and his woolen coat example.
- What three reasons does Smith give for why dividing our labor makes us more productive?
- Are our differences in talents a *cause* or a *consequence* of the division of labor? (Smith's philosopher and the porter example.)
- Why and how did we discover the division of labor? Was it a conscious choice?
- What is the difference between “real” and “nominal” price?
- What are the “component parts” of the price of commodities?
  - What differs between “rude” vs. “civilized” societies, and how does value & prices differ?
- What is the “natural price” vs. the “market price”?
- How are wages, profits, and rent determined?

#### Book II

- How does the division of labor depend on capital accumulation?
- What does Adam Smith view as “productive” vs. “unproductive” labor? Why? How does this differ from the physiocrats?
- What is capital and where does it come from? What is its purpose?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.3-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Sep 30

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday September 30.

## Tournament Votes

The first round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.