---
title: "2.4 — Thomas Malthus & The Population Principle — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, September 29, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we cover Thomas Malthus, and his theory on population, and connect it to Classical Economics.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> Thomas Malthus & *Essay on the Principle of Population* in *Reader*
- <i class="fas fas fa-book"></i> start Ch.5 "Ricardo and Malthus" in Landreth & Colander
- <i class="fas fas fa-book"></i> start Ch.3 "Population, Diminishing Returns and Rent" in Blaug

### Recommended Readings:

The following Wikipedia entries can also provide more background:


- [<i class="fab fa-wikipedia-w"></i> Thomas Malthus](https://en.wikipedia.org/wiki/Utilitarianism)
- [<i class="fab fa-wikipedia-w"></i> Jeremy Bentham](https://en.wikipedia.org/wiki/Jeremy_Bentham)
- [<i class="fab fa-wikipedia-w"></i> James Mill](https://en.wikipedia.org/wiki/James_Mill)
- [<i class="fab fa-wikipedia-w"></i> John Stuart Mill](https://en.wikipedia.org/wiki/John_Stuart_Mill)
- [<i class="fab fa-wikipedia-w"></i> William Godwin](https://en.wikipedia.org/wiki/William_Godwin)
- [<i class="fab fa-wikipedia-w"></i> Thomas Malthus](https://en.wikipedia.org/wiki/Thomas_Malthus)
- [<i class="fab fa-wikipedia-w"></i> An Essay on the Principle of Population](https://en.wikipedia.org/wiki/An_Essay_on_the_Principle_of_Population)
- [<i class="fab fa-wikipedia-w"></i> French Revolution](https://en.wikipedia.org/wiki/French_Revolution)
- [<i class="fab fa-wikipedia-w"></i> English Poor Laws](https://en.wikipedia.org/wiki/English_Poor_Laws)

### Questions to Help Your Reading

- What are Malthus’s two assumptions and what are their importance for his conclusions?

- What is the difference between population growth and growth in agriculture?

- What are Malthus’s “checks” against population?


## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.4-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Sep 30

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday September 30.

## Tournament Votes

The first round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
