---
title: "2.5 — Ricardo & Rent — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, October 4, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we begin David Ricardo’s system by primarily focusing on the idea of rent.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> David Ricardo & *The High Price of Bullion*, *On the Principles of Political Economy and Taxation* in *Reader*
- <i class="fas fas fa-book"></i> start Ch.5 "Ricardo and Malthus" in Landreth & Colander
- <i class="fas fas fa-book"></i> start Ch.4 "Ricardo's System" in Blaug

### Recommended Readings:

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> David Ricardo](https://en.wikipedia.org/wiki/David_Ricardo)
- [<i class="fab fa-wikipedia-w"></i> Corn Laws](https://en.wikipedia.org/wiki/Corn_Laws)

### Questions to Help Your Reading

- How were the theories and policy recommendations affected by the events of the era?
  - What were the Corn Laws?
  - What is the principle of comparative costs (or comparative advantage)?
- What did Ricardo view was the purpose, scope, and proper method of economics?
  - How was Ricardo’s focus different than Smith’s?
- What was Ricardo’s view on the labor theory of value?
- What is the role of capital (and capitalists), and of land (and landlords), in Ricardo’s model?
- What is rent? Where does it come from? Is it “price-determined” or “price-determining?”
  - How is the rate of rent determined?
  - What is the difference between the “intensive margin” and the “extensive margin”?
- What is profit? Where does it come from? Is it “price-determined” or “price-determining?”
- How might we describe Ricardo’s production theory with modern production functions?
- How did Ricardo integrate Malthusian population dynamics into his model?
- How does diminishing returns figure into Ricardo’s model?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.4-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 7

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 7.

## Tournament Votes

The second round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
