---
title: "2.6 — Classical Macroeconomics & Say's Law Debate — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, October 6, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we begin by wrapping up Ricardo’s distribution theory, and turn to the first great debate in the history of economics: the (macroeconomic) debate between Ricardo and Malthus over “general gluts” and Say’s law

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> Ricardo readings, Malthus *Principles of Political Economy*, Say *A Treatise on Political Economy* in *Reader*
- <i class="fas fas fa-book"></i> finish Ch.5 "Ricardo and Malthus" in Landreth & Colander
- <i class="fas fas fa-book"></i> finish Chs.3-4 "Population, Diminishing Returns, and Rent" and "Ricardo's System" in Blaug

### Recommended Readings:

- <i class="fas fas fa-book"></i> Thornton *An Enquiry into the Nature and Effects of Paper Credit of Great Britain* in *Reader*
- [<i class="fas fa-file-pdf"></i> Safner (2010), “The Duality of Say’s Law: A Restoration of J.B. Say’s Original Intentions”](/files/readings/Safner-2010.pdf) 

The second paper is my term paper in my undergraduate History of Economic Thought Class (2010) on Say’s Law (so discount appropriately!).

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Say's Law](https://en.wikipedia.org/wiki/Say%27s_law)
- [<i class="fab fa-wikipedia-w"></i> Real Bills Doctrine](https://en.wikipedia.org/wiki/Real_bills_doctrine)
- [<i class="fab fa-wikipedia-w"></i> Henry Thornton](https://en.wikipedia.org/wiki/Henry_Thornton_(reformer))
- [<i class="fab fa-wikipedia-w"></i> British Currency School](https://en.wikipedia.org/wiki/British_Currency_School)
- [<i class="fab fa-wikipedia-w"></i> Monetary-disequilibrium Theory](https://en.wikipedia.org/wiki/Monetary-disequilibrium_theory)

### Questions to Help Your Reading

- Can there be a “general glut,” a surplus (excess supply) in *all* markets at the same time?
- What is Say's Law?
- What does Malthus think of Say's Law?
- What does Ricardo think of Say's Law (and Malthus' response)?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.6-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 7

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 7.

## Tournament Votes

The second round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
