---
title: "2.7 — John Stuart Mill and the Decline of Classical Economics — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, October 13, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we cover John Stuart Mill and the "apex" and decline of the Classical School of Economics.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings:

- <i class="fas fas fa-book"></i> John Stuart Mill & *Principles of Political Economy* in *Reader*
- <i class="fas fas fa-book"></i> Ch.6 "John Stuart Mill and the Decline of Classical Economics" in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.5 in Blaug

### Recommended Readings:

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> John Stuart Mill](https://en.wikipedia.org/wiki/John_Stuart_Mill)

Since I also briefly digress into Henry George, Georgism, and the Single Value tax:

- [<i class="fab fa-wikipedia-w"></i> Wikpedia: Henry George](https://en.wikipedia.org/wiki/Henry_George)
- [<i class="fab fa-wikipedia-w"></i> Wikpedia: Georgism](https://en.wikipedia.org/wiki/Georgism)

### Questions to Help Your Reading

- What is the proper method of economics, according to Mill?

- What are Mill’s politics?

- What is the difference between production and distribution in Mill’s theory?

- What does Mill think of Say’s Law?

- How does Mill address the criticisms of economics from socialists and other critics of Ricardo?

- How much is Mill a classical economist, and how does he differ from Ricardo?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.7-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 14

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 7.

## Tournament Votes

The second round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
