---
title: "2.8 — The Marxist Challenge — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, October 18, 2022*
:::

::: {.callout-warning appearance="minimal"}
# Assignments Due

Your [1st short paper](assignments/01-short-paper) on the Classical Era is due Friday October 28 by email.
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we consider the challenges of the industrial revolution on the social fabric of Britain and the European continent: both the liberal revolutions of 1848 and the socialist critiques. We then consider Karl Marx and his economic theory, as well as the politics of Marxian-socialism.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Karl Marx & *Das Kapital* in *Reader*
- <i class="fas fas fa-book"></i> Ch.6 "Karl Marx and His Critique of Classical Economics" in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.6 in Blaug
- [<i class="fas fa-external-link-square-alt"></i> Marx and Engels, 1848, *Manifesto of the Communist Party*](https://www.marxists.org/archive/marx/works/1848/communist-manifesto/)

### Recommended Readings:

- [<i class="fas fa-file-pdf"></i> Allen (2009), “Engels’ Pause: Technical Change, Capital Accumulation, and Inequality in the British Industrial Revolution”](/readings/Allen-2009.pdf) 

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Karl Marx](https://en.wikipedia.org/wiki/Karl_Marx)
- [<i class="fab fa-wikipedia-w"></i> The Communist Manifesto](https://en.wikipedia.org/wiki/The_Communist_Manifesto)
- [<i class="fab fa-wikipedia-w"></i> Revolutions of 1848](https://en.wikipedia.org/wiki/Revolutions_of_1848)
- [<i class="fab fa-wikipedia-w"></i> Marxism](https://en.wikipedia.org/wiki/Marxism)

### Questions to Help Your Reading

- What are Marx’s motivations for his analysis?

- How does Marx’s view of socialism differ from the “utopians” like Robert Godwin?

- How much of Smith and Ricardo does Marx accept for his premises in economic analysis? Is Marx a classical economist?

- What did Marx think of Malthusian population theory?

- What is the difference between use value and surplus value?

- What is the role of the capitalist in Marxian theory?

- What is Marx’s theory of history? What is the dialectic? What is historical materialism? What are the means of production, modes of production, superstructure, and base?

- What are the “laws of capitalism” and the contradictions of capitalism?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("2.8-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 21

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 21.

## Tournament Votes

The second round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
