---
title: "3.2 — Marginal Productivity Theory — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, October 25, 2022*
:::

::: {.callout-warning appearance="minimal"}
# Assignments Due

Your [1st short paper](assignments/01-short-paper) on the Classical Era is due Friday October 28 by email.
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we continue the marginalist revolution.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Ch.9 "The Transition to Neoclassical Economics: Marginal Analysis Extended" up to Profits and Interest (p.260) in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.11 "Marginal productivity and factor prices" in Blaug

### Recommended Readings:

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Friedrich von Wieser](https://en.wikipedia.org/wiki/Friedrich_von_Wieser)
- [<i class="fab fa-wikipedia-w"></i> Eugen von Böhm-Bawerk](https://en.wikipedia.org/wiki/Eugen_von_Böhm-Bawerk)
- [<i class="fab fa-wikipedia-w"></i> John Bates Clark](https://en.wikipedia.org/wiki/John_Bates_Clark)
- [<i class="fab fa-wikipedia-w"></i> Phillip Wicksteed](https://en.wikipedia.org/wiki/Phillip_Wicksteed)
- [<i class="fab fa-wikipedia-w"></i> Francis Ysidro Edgeworth](https://en.wikipedia.org/wiki/Francis_Ysidro_Edgeworth)
- [<i class="fab fa-wikipedia-w"></i> Knut Wicksell](https://en.wikipedia.org/wiki/Knut_Wicksell)

### Questions to Help Your Reading

- How are the prices of factors of production (land, labor, capital, etc) determined?
- What is the problem of imputation?
- What is marginal (physical) product? What is average (physical) product?
- What are returns to scale? How are they different from economies of scale?
- How does the assumption of competitive markets affect the answer to many of these questions?
- What is “product exhaustion?”
- Is there a moral connation of factors of production being paid their marginal products?

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("3.2-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 28

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 28.

## Tournament Votes

The final round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
