---
title: "3.3 — Profit, Entrepreneurship, Capital, and Interest — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, October 27, 2022*
:::

::: {.callout-warning appearance="minimal"}
# Assignments Due

Your [1st short paper](assignments/01-short-paper) on the Classical Era is due Friday October 28 by email.
:::


## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we continue the marginalist revolution.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Skim Irving Fisher, Eugen von Böhm-Bawerk, (optional: Wicksell) and their readings in *Reader*
- <i class="fas fas fa-book"></i> Finish Ch.9 "The Transition to Neoclassical Economics: Marginal Analysis Extended" in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.11 "Marginal productivity and factor prices" in Blaug

### Recommended Readings:

- [<i class="fas fas fa-book"></i> Knight, Frank, 1921, *Risk, Uncertainty, and Profit*](https://www.econlib.org/library/Knight/knRUP.html)


The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Eugen von Böhm-Bawerk](https://en.wikipedia.org/wiki/Eugen_von_Böhm-Bawerk)
- [<i class="fab fa-wikipedia-w"></i> Frank Knight](https://en.wikipedia.org/wiki/Frank_Knight)
- [<i class="fab fa-wikipedia-w"></i> Irving Fisher](https://en.wikipedia.org/wiki/Irving_Fisher)
- [<i class="fab fa-wikipedia-w"></i> Fisher hypothesis](https://en.wikipedia.org/wiki/Fisher_hypothesis)
- [<i class="fab fa-wikipedia-w"></i> Intertemporal choice](https://en.wikipedia.org/wiki/Intertemporal_choice)
- [<i class="fab fa-wikipedia-w"></i> Interest](https://en.wikipedia.org/wiki/Interest)
- [<i class="fab fa-wikipedia-w"></i> Interest rate](https://en.wikipedia.org/wiki/Interest_rate)
- [<i class="fab fa-wikipedia-w"></i> Quantity Theory of Money](https://en.wikipedia.org/wiki/Quantity_theory_of_money#Fisher's_equation_of_exchange)
- [<i class="fab fa-wikipedia-w"></i> Knut Wicksell](https://en.wikipedia.org/wiki/Knut_Wicksell)
- [<i class="fab fa-wikipedia-w"></i> Cumulative process](https://en.wikipedia.org/wiki/Cumulative_process)

### Questions to Help Your Reading

#### On Profit and Uncertainty

- Is entrepreneurship a fourth factor of production that is paid its marginal product?
- In what way is pure profit a “residual”?
- What is the difference between “risk” and “uncertainty” according to Knight?
- How is profit related to uncertainty?
- What are the main differences between the *theory* of (perfect) competition, and *actual* competition in the real world? How is this tied in with uncertainty, and with profit?

#### On Interest

- What are Böhm-Bawerk’s three reasons for a positive rate of interest?
- What is “roundaboutness” in production? Why is it more productive, according to Böhm-Bawerk?
- What is “time preference”?
- How does Fisher conceive of interest as it relates to income, and capitalized values? 
- What is the quantity theory of money, and Fisher’s equation of exchange? What are the main takeaways?
- What is the difference between the “natural rate” and the “market rate” of interest, according to Wicksell? Explain Wicksell’s “cumulative process” that results if the two are different.

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("3.2-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Oct 28

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday October 28.

## Tournament Votes

The final round of the Pre-Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
