---
title: "3.5 — Marshallian Economics II: Cost & Supply — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, November 1, 2022*
:::


## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we continue the marginalist revolution.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Finish Ch.10 "Alfred Marshall and Neoclassical Economics" in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.10 "Marshallian Economics: Cost and Supply" in Blaug

### Recommended Readings:

- [<i class="fas fas fa-book"></i> Marshall, Alfred, 1920 (1890), *Principles of Economics* (8th ed.)](https://www.econlib.org/library/Marshall/marP.html)

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Alfred Marshall](https://en.wikipedia.org/wiki/Alfred_Marshall)
- [<i class="fab fa-wikipedia-w"></i> Tax incidence](https://en.wikipedia.org/wiki/Tax_incidence)
- [<i class="fab fa-wikipedia-w"></i> Long run and short run](https://en.wikipedia.org/wiki/Long_run_and_short_run)
- [<i class="fab fa-wikipedia-w"></i> Fixed cost](https://en.wikipedia.org/wiki/Fixed_cost)
- [<i class="fab fa-wikipedia-w"></i> Variable cost](https://en.wikipedia.org/wiki/Variable_cost)
- [<i class="fab fa-wikipedia-w"></i> Cost curve](https://en.wikipedia.org/wiki/Cost_curve)
- [<i class="fab fa-wikipedia-w"></i> Quasi-rent](https://en.wikipedia.org/wiki/Quasi-rent)
- [<i class="fab fa-wikipedia-w"></i> Economies of scale](https://en.wikipedia.org/wiki/Economies_of_scale)
- [<i class="fab fa-wikipedia-w"></i> Economies of scale in Marshall](https://en.wikipedia.org/wiki/Economies_of_scale#Economies_of_scale_in_Marshall)
- [<i class="fab fa-wikipedia-w"></i> Quantity Theory of Money (Cambridge Approach)](https://en.wikipedia.org/wiki/Quantity_theory_of_money#Cambridge_approach)

### Questions to Help Your Reading

- What are the four “periods” (or “runs”) according to Marshall? What is different about the supply curve in each?
- What do you recognize from your principles & intermediate microeconomics courses from Marshall?
- What is a “quasi-rent”? Why does it only exist in the short run?
- What is a constant-cost, increasing-cost, and decreasing-cost industry?
- What are interval vs. external economies of scale? What are the implications for competition vs. monopoly?
- How does Marshall’s view of money and the quantity theory differ from Fisher?

### Questions to Help Your Reading

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("3.5-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Nov 4

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday November 4.

## Tournament Votes

The first round of the Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
