---
title: "3.7 — Welfare Economics — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, November 9, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

Today we wrap up Neoclassical economics with a discussion of welfare economics, both in the British Marshallian tradition and in the Italian Walrasian tradition.

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> End of Ch.11 "Walras and General Equilibrium Theory" (on Pareto) in Landreth & Colander
- <i class="fas fas fa-book"></i> Ch.13 "General Equilibrium and Welfare Economics" in Blaug

### Recommended Readings:

- [<i class="fas fa-file-pdf"></i> Blaug, 1996, "The Marginal Conditions" excerpt  pp.577-579](/readings/Blaug-1996-marginal-conditions.pdf)
- [<i class="fas fa-file-pdf"></i> Humphrey, 1996, "The Early History of the Box Diagram"](/readings/Huphrey-1996.pdf)
- [<i class="fas fa-file-pdf"></i> Persky, 2002, "Retrospectives: Pareto’s Law"](/readings/Persky-2002.pdf)
- [<i class="fas fa-file-pdf"></i> Colander, 2007, "Retrospectives: Edgeworth's Hedonimeter and the Quest to Measure Utility"](/readings/Colander-2007.pdf)
- [<i class="fas fa-file-pdf"></i> Gabaix, 2016, "Power Laws in Economics"](/readings/Gabaix-2016.pdf)

The following Wikipedia entries can also provide more background:

- [<i class="fab fa-wikipedia-w"></i> Francis Ysidro Edgeworth](https://en.wikipedia.org/wiki/Francis_Ysidro_Edgeworth)
- [<i class="fab fa-wikipedia-w"></i> Edgeworth Box](https://en.wikipedia.org/wiki/Edgeworth_box)
- [<i class="fab fa-wikipedia-w"></i> Vildredo Pareto](https://en.wikipedia.org/wiki/Vildredo_Pareto)
- [<i class="fab fa-wikipedia-w"></i> Pareto principle](https://en.wikipedia.org/wiki/Pareto_principle)

- [<i class="fab fa-wikipedia-w"></i> Arthur Cecil Pigou](https://en.wikipedia.org/wiki/https://en.wikipedia.org/wiki/Arthur_Cecil_Pigou)
- [<i class="fab fa-wikipedia-w"></i> Welfare economics](https://en.wikipedia.org/wiki/https://en.wikipedia.org/wiki/Welfare_economics)
- [<i class="fab fa-wikipedia-w"></i> Fundamental theorems of welfare economics](https://en.wikipedia.org/wiki/Fundamental_theorems_of_welfare_economics)

### Questions to Help Your Reading

- What are indifference curves?

- What is the contract curve?

- What does a “determinate” vs. an “indeterminate” outcome of exchange mean?

- Explain the Edgeworth box.

- What is a Pareto improvement? What does Pareto optimal mean?

- What are the two fundamental theorems of welfare economics?

- What are the marginal conditions at an optimum?
## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("3.7-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Nov 4

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday November 4.

## Tournament Votes

The first round of the Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
