---
title: "4.3 — The Evolution of Modern Microeconomics  — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, November 17, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

One of the implications of neoclassical economics is that we have discovered all of the optimal conditions — in production, in consumption, and in exchange — for maximizing the value of resources for society. Markets and a market-based economy have lots of problems but we know the optimal results they can achieve. So, since economists have discovered the optimal conditions for resource allocation, why can't the government just replace the market to efficiently allocate resources? It will achieve the same results as a market equilibrium, and arguably for the better, since it can avoid the problems with markets!

This claim, coupled with the fact that in the late 1910s a major European power undergoes a revolution where the victors *try to establish* a socialist society, constitutes the focus of the "socialist calculation debate." How would a socialist economy and society actually operate? Is it superior to market-based economy and society?

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Ch.14 "The Development of Modern Microeconomic Theory" in Landreth & Colander

### Recommended Readings:

- [<i class="fas fa-file-pdf"></i> Buchanan (1964), "What Should Economists Do"](/files/readings/Buchanan-1964.pdf)
- [<i class="fas fa-file-pdf"></i> Boulding (1971), "After Samuelson, Who Needs Adam Smith?"](/files/readings/Boulding-1971.pdf)
- [<i class="fas fa-file-pdf"></i> Boettke (1997), "Where Did Economics Go Wrong: Modern Economics as a Flight from Reality, "](/files/readings/Boettke-1997.pdf)

### Questions to Help Your Reading

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("4.3-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Nov 18

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday November 18.

## Tournament Votes

The first round of the Classical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
