---
title: "4.4 — The Keynesian Revolution — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Tuesday, November 29, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> “Keynesian Macroeconomics” in Ch.15 "The Development of Modern Macroeconomic Thought" in Landreth & Colander

### Recommended Readings:

- [<i class="fas fa-podcast"></i> NPR's *Planet Money*: "The Invention of the Economy"](https://www.npr.org/sections/money/2014/03/05/286366404/episode-521-the-invention-of-the-economy)
- [<i class="fas fas fa-book"></i> Keynes, 1936, *The General Theory of Employment, Interest and Money*](https://www.marxists.org/reference/subject/economics/keynes/general-theory/)

### Helpful:

- [<i class="fab fa-wikipedia-w"></i> John Maynard Keynes](https://en.wikipedia.org/wiki/John_Maynard_Keynes)
- [<i class="fab fa-wikipedia-w"></i> The General Theory of Employment, Interest and Money](https://en.wikipedia.org/wiki/The_General_Theory_of_Employment,_Interest_and_Money)
- [<i class="fab fa-wikipedia-w"></i> Keynesian Revolution](https://en.wikipedia.org/wiki/Keynesian_Revolution)
- [<i class="fab fa-wikipedia-w"></i> Keynesian economics](https://en.wikipedia.org/wiki/Keynesian_Revolutionhttps://en.wikipedia.org/wiki/Keynesian_economics)

### Questions to Help Your Reading

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("4.4-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Dec 2

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday December 2.

## Tournament Votes

The first round of the Neoclassical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
