---
title: "4.5 — The Evolution of Modern Macroeconomics — Class Content"
execute:
  freeze: auto
---

```{r, echo = F}
source(here::here("slides", "slide-links.R"))
```

::: {.callout-note appearance="minimal"}
# Meeting Dates

*Thursday, December 2, 2022*
:::

## <i class="fas fa-info-circle fa-lg"></i> Overview

## <i class="fas fa-book-reader fa-lg"></i> Readings

### Required Readings

- <i class="fas fas fa-book"></i> Finish Ch.15 "The Development of Modern Macroeconomic Thought" in Landreth & Colander

### Recommended Readings:

- [<i class="fab fa-youtube"></i> "Fear the Boom and Bust: Keynes vs. Hayek - The Original Economics Rap Battle!"](https://www.youtube.com/watch?v=d0nERTFo-Sk)
- [<i class="fab fa-youtube"></i> "Fight of the Century: Keynes vs. Hayek - Economics Rap Battle Round Two"](https://www.youtube.com/watch?v=GTQnarzmTOc)
- [<i class="fab fa-youtube"></i> "Game of Theories: The Keynesians," *MR University*](https://mru.org/courses/principles-economics-macroeconomics/business-cycle-theories-keynesian)
- [<i class="fab fa-youtube"></i> "Game of Theories: The Monetarists," *MR University*](https://mru.org/courses/principles-economics-macroeconomics/business-cycles-monetarists)
- [<i class="fab fa-youtube"></i> "Game of Theories: Real Business Cycles," *MR University*](https://mru.org/courses/principles-economics-macroeconomics/business-cycles-real-business-cycle)
- [<i class="fab fa-youtube"></i> "Game of Theories: The Austrians," *MR University*](https://mru.org/courses/principles-economics-macroeconomics/business-cycles-austrian-economic-theory)
- [<i class="fab fa-youtube"></i> "Game of Theories: The Great Recession," *MR University*](https://mru.org/courses/principles-economics-macroeconomics/business-cycles-great-recession)

### Questions to Help Your Reading

## <i class="fas fa-chalkboard-teacher"></i> Slides

Below, you can find the slides in two formats. Clicking the image will bring you to the html version of the slides in a new tab. The lower button will allow you to download a PDF version of the slides.

::: callout-tip
You can type <kbd>h</kbd> to see a special list of viewing options, and type <kbd>o</kbd> for an outline view of all the slides.
:::

I suggest printing the slides beforehand and using them to take additional notes in class (*not everything* is in the slides)!

```{r}
#| echo: false
#| output: asis

slide_links("4.5-slides")
```

## <i class="fas fa-laptop-code"></i> Assignments

### Participation/Discussion Board Posts Due 8 PM Fri Dec 2

This week's graded discussion is worth 5 points, and can be a combination of discussion in class, and/or posts on the Blackboard Discussion Board by 8 PM this Friday December 2.

## Tournament Votes

The first round of the Neoclassical division of the "Most Interesting Economist in History" tournament is live. Please post your votes in the discussion board.
